---
title: "Part 2: Twitter Research Workflow"
subtitle: "#AECT20 workshop"
author: "K. Bret Staudt Willet, Spencer P. Greenhalgh, & Joshua M. Rosenberg"
date: "October 30, 2020"
output:
  xaringan::moon_reader:
    lib_dir: libs
    seal: true
    css: [default, 'custom.css', 'custom-fonts.css']
    nature:
      titleSlideClass: [left, bottom]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

library(knitr)
library(xaringan)
library(tidyverse)
```

class: inverse, center, middle

# Welcome back!

---

# Important Links

## Homebase

```{r child="chunks/homebase.Rmd"} 
```

## Agenda

```{r child="chunks/agenda.Rmd"} 
```

---

# Need help? Reach out!

```{r child="chunks/help-slides.Rmd"} 
```

---

class: inverse, center, middle

#  {tidytags}

**Simple Collection and Powerful Analysis of Twitter Data**

https://bretsw.github.io/tidytags/

---

# Try it out!

Let's hop over to the **Demo Doc for Part 2**!

- [Working in RStudio Cloud](https://rstudio.cloud/project/1820768)
- [Working locally](2-workflow-demo-doc.Rmd)

---

class: inverse, center, middle

# Discuss in groups!

**(Five minutes in groups, five minutes together)**

- What challenges did you encounter?
- What successes did you encounter?
- What questions do you still have?

---

class: inverse, center, middle

# THANK YOU!

---

# Stay Connected

### Bret Staudt Willet, ABD

- Ph.D. Candidate, Educational Psychology & Educational Technology, Michigan State University
- http://bretsw.com
- Twitter: [@bretsw](https://twitter.com/bretsw)

### Spencer Greenhalgh, Ph.D.

- Assistant Professor, Information Communication Technology, University of Kentucky
- https://spencergreenhalgh.com
- Twitter:[@spgreenhalgh](https://twitter.com/spgreenhalgh)

### Josh Rosenberg, Ph.D.

- Assistant Professor, STEM Education, University of Tennessee, Knoxville
- https://joshuamrosenberg.com
- Twitter: [@jrosenberg6432](https://twitter.com/jrosenberg6432)

---

# Resources

```{r child="chunks/resources.Rmd"} 
```

---

# Troubleshooting

```{r child="chunks/troubleshooting.Rmd"} 
```